---
title       : Getting started with SpaDES
description : This chapter introduces the SpaDES package for simulation modelling in R.

--- type:NormalExercise lang:r xp:50 skills:1 key:5ebcc6f8f3
## Install SpaDES and its dependencies

Before we begin, we need to ensure we have installed the latest development version of the `SpaDES` package.
Note that `SpaDES` requires R version `3.2.2` or greater.

*** =instructions
- Install the `SpaDES` package from CRAN.
- Check the `SpaDES` package version number.

*** =hint
- Use `install.packages()` for the first instruction.
- Use `packageVersion()` for the second instruction.

*** =sample_code
```{r}
# install the SpaDES package from CRAN


# determine the SpaDES package version from CRAN

```

*** =solution
```{r}
# install the SpaDES package from CRAN
dir.create("~/R")
.libPaths("~/R")
install.packages("SpaDES", repos = "https://cloud.r-project.org/")

# determine the SpaDES package version from CRAN
packageVersion("SpaDES")
```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki

test_function("install.packages", args = "pkgs")
test_function("packageVersion", args = "pkg")

test_error()

success_msg("Good work!")
```
